Andres Karjus

### 2019-02-02 index.Rmd
twitter widget added

#### Recent publications

@@

<details><summary> &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Show all...</summary>

@@

#### Recent conferences & seminars

@@

---

<a class="twitter-timeline" data-width="400" data-height="300" href="https://twitter.com/AndresKarjus?ref_src=twsrc%5Etfw">Tweets by AndresKarjus</a> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

>>>>

#### Publications

@@

<details><summary> &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Show older...</summary>

@@

#### Conferences & seminars

@@

---
<br>

#### Recent tweets

<a class="twitter-timeline" 
  data-show-screen-name="false" data-lang="en" 
  data-width="400" 
  data-height="250" 
  href="https://twitter.com/AndresKarjus?ref_src=twsrc%5Etfw"
  data-chrome="noheader nofooter noborders">
  " "
</a> 
<script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>
